The National Eutrophication Survey: lake characteristics and historical nutrient concentrations

### 2017-11-06 08_manuscript/template.tex
insert inline figures

@@

@@

>>>>

\begin{figure*}[t]
  \includegraphics[width=12cm]{points_regions-crop.pdf}
  \caption{Survey locations colored by sampling year (1972 northeastern-red, 1973 southeastern-green, 1974 central-blue, 1975 western-grey).}
\end{figure*}

@@

% insert table 1

@@

% insert table 2

\begin{figure*}[t]
  \includegraphics[width=12cm]{alkalinity-crop.pdf}
  \caption{Map of log-scaled alkalinity (mg/L) interpolated using inverse distance weighting.}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{secchi-crop.pdf}
  \caption{Map of secchi depth (m) interpolated using inverse distance weighting.}
\end{figure*}
